---
title: "Introduction to SLEAC"
subtitle: Simplified Lot Quality Assurance Sampling Evaluation of Access and Coverage
author: Mark Myatt
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SLEAC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(sleacr)
```

**Simplified LQAS (Lot Quality Assurance Sampling) Evaluation of Access and Coverage (SLEAC)** is a low-resource method for classifying the coverage of selective feeding programmes. It was designed for use in programmes delivering CMAM services over many service delivery units. Examples of such programs include:

* National or regional programs delivering CMAM services through health districts; and,

* District programs delivering CMAM services through primary health care centres.

**SLEAC** surveys classify coverage at the level of the service delivery unit. This will vary with the scale of the programme. For example:

* In the case of a national or regional program delivering CMAM services through health districts (or the equivalent local administrative unit) the service delivery unit is the heath district;

* In the case of a district program delivering CMAM services through primary healthcare centres the service delivery unit is the primary healthcare centre

It is not usually sensible to treat units larger than a health district as a service delivery unit.

SLEAC may also be used to estimate coverage over wide areas. SLEAC has been used for regional and national coverage surveys. In these surveys coverage is usually classified and mapped at the district level and estimated at the regional and national levels.

## Classifying coverage

The SLEAC method classifies program coverage for a service delivery unit such as a health district. A SLEAC survey does not provide an estimate of overall coverage with a confidence interval for a single service delivery unit. Instead, a SLEAC survey identifies the category of coverage (e.g. low, moderate, or high) that best describes the coverage of the service delivery unit being assessed. The advantage of this approach is that relatively small sample sizes (e.g. `n = 40`) are required in order to make accurate and reliable classifications.

SLEAC uses the lot quality assurance sampling (LQAS) classification technique.

* The SLEAC survey sample is designed to represent an entire service delivery unit such as a district.
      
* A target sample size for SLEAC surveys is decided in advance of data-collection. This  is usually about `n = 40` SAM cases.

* SLEAC surveys may classify coverage into three (or more) classes.
