---
title: "Introduction to sleacr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(sleacr)
```

**Simplified LQAS (Lot Quality Assurance Sampling) Evaluation of Access and Coverage (SLEAC)** is a low-resource method for
classifying the coverage of selective feeding programmes. It was designed for use in programmes delivering CMAM services over many service delivery units. Examples of such programs include:

* National or regional programs delivering CMAM services through health districts; and,
* District programs delivering CMAM services through primary health care centres.

**SLEAC** surveys classify coverage at the level of the service delivery unit. This will vary with the scale of the programme. For example:

* In the case of a national or regional program delivering CMAM services through health districts (or the equivalent local administrative unit) the service delivery unit is the heath district;

* In the case of a district program delivering CMAM services through primary healthcare centres the service delivery unit is the primary healthcare centre

